Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-14 latex/comp_or.tex
minCGdev optimized

\multirow{6}{*}{$1.2$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 11.22}   &{\it 7.88}   &{\it 10.25} &{\it 13.34}  &{\it 14.30}   &{\it 12.92}       & 1.00 \\% 6845

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 9.66         &  6.38       &  9.55       &  11.12      &  12.37      &   12.03      & 0.89 \\% 6111
&                                                & {\it run time (s)} &  < 1         &  5          &    11       &   43        &  128        &  835         &  1.0 \\% 1023

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & 11.03        & 7.43        & 10.05       & 13.08       & 14.02       &  12.66       & 0.99\\% 6827

&                                                & {\it run time (s)} &  < 1         &  2          &    4        &  15         &  47         & 295          &  {\bf 2.8}\\% 364

@@

\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 15.17}   &{\it 10.98}  &{\it 17.80}  &{\it 16.92}  &{\it 19.63}   &{\it 18.62}  & {\it 1.00} \\% 9912

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                & 13.70        &  9.07       &  13.70      &  15.43      &   17.19     &  17.24       & 0.87 \\%8633
&                                                & {\it run time (s)} &  < 1         &  4          &    7        &   26        &   81        &  520         & 1.0\\% 639

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                & 14.82        & 10.45       & 17.45       &{\bf 16.92}  & 19.27       & 18.30        & 0.98\\%9721
&                                                & {\it run time (s)} &  < 1         &  2          &    3        &    12       &   38        &   236        & {\bf 2.2}\\% 292

\midrule
\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 23.11}   &{\it 16.74}  &{\it 23.63}  &{\it 24.33}  &{\it 26.22}  &{\it 25.80}   & {\it 1.00} \\% 13983

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                       & $f$                &   20.42      &   13.90     &  20.30      &  22.96      &   25.28     &   24.81      & 0.91\\% 12767
&                                                & {\it run time (s)} &  2           &  9          &    17       &   68        &   206       &  1216        & 1.0\\% 1518

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                     & $f$                &  22.66       &  15.41      &  23.17      &  23.37      &  23,91      &  25.25       &  0.96\\% 13377
&                                                & {\it run time (s)} &  2           &  3          &    5        &   20        &   64        &  398         & {\bf 2.8}\\% 544

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results}  \label{tab:results2}
	\footnotesize
	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &  {\bf Resolution}   &                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    & {\it method}        & {\bf Results}                &{\bf 1}      &{\bf 2}      &{\bf 3}      &{\bf 4}      &{\bf 5}       &{\bf 6}      &{\bf Speedup} \\
		\toprule

		\multirow{6}{*}{$1.2$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 12.02}   &{\it 8.74}   &{\it 12.56} &{\it 14.34}  &{\it 14.79}   &{\it 13.49}       & 1.00 \\%

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &  10.34       & 8.50        & 12.42      &  15.06      &  15.97       &  15.88       &   \\% 
		&                                                & {\it run time (s)} &  < 1         &  3          &  5         &   20        &  58          &  352         &  1.0 \\%

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &  11.76       &  8.57       & 12.28      &  14.02      &  14.50       & 13.23        & \\%

		&                                                & {\it run time (s)} &  < 1         &  2          &  3         &   47        &  33          & 193         &  {\bf 2.8}\\%

@@

		\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 15.17}   &{\it 10.98}  &{\it 17.80}  &{\it 16.92}  &{\it 19.63}   &{\it 18.62}  & {\it 1.00} \\% 9912

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &         &         &       &        &        &         &  \\%8633
		&                                                & {\it run time (s)} &  < 1         &  4          &    7        &   26        &   81        &  520         & 1.0\\% 639

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &         &        &        &  &        &         & \\%9721
		&                                                & {\it run time (s)} &  < 1         &  2          &    3        &    12       &   38        &   236        & {\bf 2.2}\\% 292

		\midrule
		\multirow{6}{*}{$2.0$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 23.11}   &{\it 16.74}  &{\it 23.63}  &{\it 24.33}  &{\it 26.22}  &{\it 25.80}   & {\it 1.00} \\% 13983

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &         &        &        &        &        &         & \\% 12767
		&                                                & {\it run time (s)} &  2           &  9          &    17       &   68        &   206       &  1216        & 1.0\\% 1518

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &         &        &        &        &        &         &  \\% 13377
		&                                                & {\it run time (s)} &  2           &  3          &    5        &   20        &   64        &  398         & {\bf 2.8}\\% 544

@@

We were lucky that {\it mpShims} touched the edge of the polyhedron that bounds the feasible region, it found the optimal solution in volume $surplus = 1.5$, scenario {\bf 4}.

{\it mpShims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, mpShims was 2.6 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the execution {\it race condition} management limited {\it mpShims} performance.

@@

\subsection{Yet another improvement}
\label{improvement}

@@

Columns {\bf Before} and {\bf After} on Table \ref{tab:distRampDoor} refer to the application of the integer programming solver according to equations \ref{eq:distobj} to \ref{eq:disttorque}. Column {\bf Improvement} is the percentage of improvements in distances minimization.

% \ref{eq:distobj} to \ref{eq:disttorque}

\begin{table}[H]
\centering
\caption{Minimization of pallets distances from the ramp door}  \label{tab:distRampDoor}
\footnotesize
%\scriptsize
\begin{tabular}{ccccc}
\toprule

{\it surplus} & {\bf Scenario} & {\bf Before (m)} & {\bf After (m)}  & {\bf Improvement (\%)}  \\
\midrule
\multirow{6}{*}{$1.2$}& 1 &  32 &  32 & 0.0 \\
&                       2 & 181 & 181 & 0.0 \\
&                       3 & 149 & 149 & 0.0\\
&                       4 & 131 & 131 & 0.0  \\
&                       5 & 113 & 113 & 0.0  \\
&                       6 & 105 & 105 & 0.0 \\
\midrule
\multirow{6}{*}{$1.5$}& 1 &  &  &  \\
&                       2 &  &  &  \\
&                       3 &  &  &  \\
&                       4 & 123 & 92 & 25.3  \\
&                       5 &  &  &  \\
&                       6 &  &  &  \\
\midrule
\multirow{6}{*}{$2.0$}& 1 &  &  &  \\
&                       2 &  &  &  \\
&                       3 &  &  &  \\
&                       4 &  &  &  \\
&                       5 &  &  &  \\
&                       6 &  &  &  \\
\midrule
&                         &        & {\bf Average} & {\bf 29}\\
\bottomrule	
\end{tabular}
%\textsuperscript{asdf sd .}	
\normalsize
\end{table}

This last procedure favored ground operations as it reduced in 29\% the distances pallets will be moved on disembarking operations. This last step is not part of {\it mpShims} and may be applied as a post improvement for any method. This is another important contribution of this work.

@@

We added another important contribution by favoring ground operations reducing in 29\%, in average, the distances pallets will be moved on disembarking operations, our second contribution.

>>>>

		\multirow{6}{*}{$1.2$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 12.23}&{\it 8.67} &{\it 12.67}&{\it 15.36}&{\it 16.29}&{\it 16.20}&  \specialcell{{\bf 1.00}\\-} \\%  8142

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &     10.34 &     8.50  &     12.42 &     15.06 &     15.97 &     15.88 &  0.96 \\% 7817
		&                                                & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.0 \\% 439

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &     11.73 &     7.57  &     12.05 &     12.95 &     13.94 &     13.62 & 0.88 \\% 7186

		&                                                & {\it run time (s)} &     < 1   &     2     &     3     &     16    &     33    &     193   &  {\bf 1.8}\\% 248

@@

		\multirow{6}{*}{$1.5$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it }&{\it  } &{\it  }&{\it  }&{\it  }&{\it  }&  \specialcell{{\bf 1.00}\\-} \\%

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}                       & $f$                &     14.68 &   12.21   &  17.67    &  21.01    &  22.64    &       &    \\% 
        &                                                & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &        &  1.0 \\%

        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $mpShims$}                     & $f$                &       &        &       &       &       &       &   \\% 7186
        &                                                & {\it run time (s)} &     < 1   &     2     &     3     &     16    &     33    &     193   &  {\bf 1.8}\\% 248

@@

@@

{\it Shims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, {\it mpShims} was 1.8 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the execution {\it race condition} management limited {\it mpShims} performance.

@@

After this inclusion {\it Shims} results surpassed that of {\it mpShims}. In multi-processing mode ({\it mpShims}) this inclusion (line \ref{mpShims:minCGdev}) made a negligible difference.

\subsection{Another possible improvement}
\label{improvement}

@@

There was some expectation on this post-improvement method as it could have minimized the distances of travel of the pallets to the ramp door, but unfortunately, there was no alteration to these distances.

@@
